The watershed transform in ITK - discussion and new developments

### 2006-01-11 article/watershed_paper.tex
move parper to article dir
darcs-hash:20060111173128-2fc9d-bcb6183a2aec08a32328edb2f630117e36dcb1eb.gz

>>>>

Preventing boundary checks - not really the itk way, but if a user is
willing to throw away the image border by treating it as a watershed
line then there is no need to test for boundary conditions. There
isn't even any need to use the face calculator approach because border
pixels will be initially tagged as processed, and therefore we can be
certain their neighbors are never checked.
